Motional Ground State Cooling Outside the Lamb-Dicke Regime

### 2017-07-25 paper.tex
Axis renaming
Overall survival line

    (B,C) Rabi flopping on axis 3 (B) carrier and (C) first order heating sideband

@@

@@

>>>>

    (B,C) Rabi flopping on axis $y$ (B) carrier and (C) first order heating sideband

@@

    The horizontal dashed line shows the overall survival after cooling and imaging.

@@

    Similar to the radial plot,
    the horizontal dashed line shows the overall survival after cooling and imaging.
